---
title: "SIVOCS Interview Candidates"
runningheader: "Selection Criteria" # only for pdf output
subtitle: "" # only for html output
author: ""
date: "`r Sys.Date()`"
output:
  tufte::tufte_book:
    citation_package: natbib
    latex_engine: xelatex
    keep_tex: true
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
  tufte::tufte_html: default
bibliography: skeleton.bib
link-citations: yes
---

```{r setup, include=FALSE}
library(tufte)
library(ggplot2)
library(tidyr)
library(scales)
library(ggthemes)
library(ggthemr)
library(gridExtra)
library(stringr)
library(PerformanceAnalytics)

# invalidate cache when the tufte version changes
knitr::opts_chunk$set(cache.extra = packageVersion('tufte'))
options(htmltools.dir.version = FALSE)
# why do I even have to do this
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```


```{r include=FALSE}
df_ult <- readRDS("./df_ult.RDS")
source("./02_analysis/02_static_responses.R")

```

# Selection Steps

The selection of ~60 candidates for the interview process has been carried out with a clustering approach. Each of the clusters has been arranged with consideration of some of the most central variables in identifying Social Innovation (SI) which have been determined previously in the study.

The distribution of some of the important variables as well as their correlations with each other can be seen in the Figure \@ref(fig:corr).

```{r corr, echo=FALSE, message=FALSE, warning=FALSE}
chart.Correlation(data[, c("contribToSI.rate.", "familiarWithSI.response.", "transdisciplinaryExp.rate.", "motivation.welfare.","groupsInvolved.citiz.")], histogram=TRUE, pch=19)
```

## Step 1: Contribution to SI (self-assessment)

The first criterion was selected to find easily identifiable (obvious) SI-related projects. The selection has relied on the self-assessment of the participants about the contribution their specific project made to the SI.

The selected 34 (28m | 6f) participants are lying between the 3rd quantile (8) and maximum value (10) on the scale of the variable *contribution to SI*, the distribution of the variable can be seen in Figure\@ref(fig:step1). 

```{r step1, echo=FALSE, message=FALSE, warning=FALSE}
ggthemr("fresh")
ggplot(data, aes(x=contribToSI.rate.))+
  geom_bar()+
  scale_x_continuous(breaks= pretty_breaks())
```

## Step 2: Experience with transdisciplinarity, contribution to SI, sci. disciplines
After excluding the selected participants in the previous step the participants who have placed themselves between the 3rd quantile (8) and maximum value (10) on the variable *experience with transdisciplinarity* selected for step 2. The first examination included fitting a linear regression model to investigate the relation between *experience with transdisciplinarity* and *contribution to SI*. A visualisation regarding this model can be seen in Figure \@ref(fig:td_si_lm)^[Caution: The figure includes the whole sample, not just the reduced sample after excluding the chosen participants in step 1.].


```{r td_si_lm, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(data=data, aes(x=contribToSI.rate., y=transdisciplinaryExp.rate.))+
  geom_point()+
  geom_smooth(method="lm") 

```

While transdisciplinarity shows some relation to SI, its meaning can be different among different disciplines. The cluster in the second step has been divided into *STEM* and *other disciplines* before examining further.

The examination of the participants from *STEM* disciplines with high disciplinarity experience included along with *contribution tho SI* the analysis of the *motivation* for the study (e.g. either human condition/welfare was part of the motivation) and which other societal actors were involved in the project. Finally, because of the unsatisfactory representation of the female participants in the cluster, a slight bias toward female participants from STEM fields has been added. This examination yielded 3 candidates for the interview process (2m | 1f).

Non-STEM fields were also subjected to a similar analysis regarding *contribution to SI* and different kinds of involvements. A manual examination was also needed because of the large spectrum of those disciplines. 19 participants have been selected in this cluster in total (4f | 15m)

## Step 3: Motivation to improve the human condition/welfare, involvement of the civil society, civil soc.'s nature of the involvement

Variables *motivation to improve the human condition* and *rate of involvement of the civil soc.* do not necessarily show a strong correlation (see Figure \@ref(fig:wf_fi_lm)). However, including the *nature of involvement* of civil society groups yields relatively better results (*nature of involvement* collaboration or cocreation against the other forms of collaboration is described in the second figure). Therefore, step 3 has focused on the projects with high motivation to improve human condition and citizen involvement where the nature of the involvement is either collaboration or co-creation. This approach yielded 7 participants (1f | 6m).

```{r wf_gi_lm, echo=FALSE, message=FALSE, warning=FALSE}
data$collaboration <- factor(data$natureOfInvolvement.citiz. %in% c('cocr' , "collab"))

cocr <- ggplot(data=data, aes(x=motivation.welfare., y=groupsInvolved.citiz., colour= collaboration))+
  geom_point()+
  geom_smooth(method="lm") +
  labs(color = "cit. cocrea./collab.") +
  theme(legend.title = element_text( size=4), legend.text=element_text(size=4))

colla <- ggplot(data=data, aes(x=motivation.welfare., y=groupsInvolved.citiz., colour= factor(natureOfInvolvement.citiz. == 'colla')))+
  geom_point()+
  geom_smooth(method="lm") +
  labs(color = "cit. collab.") +
  theme(legend.title = element_text( size=2), legend.text=element_text(size=2))
norm <- ggplot(data=data, aes(x=motivation.welfare., y=groupsInvolved.citiz.))+
  geom_point()+
  geom_smooth(method="lm") 

norm
cocr
```

## Step 4: Familiarity with SI

Considering the observations in the study correspond to the projects and not the researchers themselves, it is fairly possible to overlook researchers with SI experience and SI-related (SNF-funded) projects just because the specific project was not necessarily an SI-related project. In order to combat this issue step 4 started with the consideration of high values (again between 3rd quantile and max values) of *familiarity with SI*.  

```{r step4, echo=FALSE, message=FALSE, warning=FALSE}
ggthemr("fresh")
ggplot(data, aes(x=familiarWithSI.response.))+
  geom_bar()+
  scale_x_continuous(breaks= pretty_breaks())
```

This relatively small cluster has been also analyzed manually with the consideration of answers to open and meta-questions like *feedback*, *title of the project* etc., some of the participants were specially selected for their critical feedback on the nature of the study. This process added 8 more participants to the list. 

# Final

After a manual elimination, from the 71 selected projects in total 16 relatively less related projects are eliminated, **leaving 55 participants in total** (14f | 41 ~ 25%, see Figure \@ref(fig:gender)).

```{r gender, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(df_ult, aes(x=factor(gender), fill=factor(gender)))+
  geom_bar()+
  scale_x_discrete(breaks= pretty_breaks())
```

Also, the distribution of the sci. disciplines in the final sample is as follows:

```{r warning=FALSE, , echo=FALSE}
##ggplot(df_ult, aes(x=discipline))+
##  geom_bar()+
##  #theme_fivethirtyeight()+
##  #theme_calc()+
##  scale_x_discrete(breaks= pretty_breaks())
library(knitr)
kable(table(df_ult$discipline))
```