---
title: "SIVOCS Hypothesis Testing"
runningheader: "" # only for pdf output
subtitle: "" # only for html output
author: ""
date: "`r Sys.Date()`"
output:
  tufte::tufte_html: default
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
  tufte::tufte_book:
    citation_package: natbib
    latex_engine: xelatex
bibliography: skeleton.bib
link-citations: yes
---

```{r setup, include = FALSE}
library(tufte)
# invalidate cache when the tufte version changes
knitr::opts_chunk$set(
	message = FALSE,
	warning = FALSE,
	cache.extra = packageVersion("tufte")
)
options(htmltools.dir.version = FALSE)
library(dplyr)
library(ggplot2)
library(magrittr)
library(ggplot2)
library(PerformanceAnalytics)
library(psych)
library(corrplot)
library(nFactors)
library(kableExtra)
require(ggiraph)
require(ggiraphExtra)
require(plyr)
library(sjPlot)
library(sjmisc)
library(sjlabelled)

setwd("../../utku_SIVOCS/")
# Data Frame
source("./02_analysis/02_static_responses.R")
# colnames of the specific question groups
source("./02_analysis/99_question_groups.R")
```



# Example 1: A1 | Problem: Explaining a 3. unknown variable with the relation between 2 variables
```{r produceDFs, include = FALSE}
# A1 | E1, D1.2, D1.3, D2.3?
a1.df <- data[, c(a1.colnames, e1.colnames, d1.colnames[2:3], d2.colnames)]
a1e1.df <- data[, c(a1.colnames, e1.colnames)]

```

Hypothesis: Transdisciplinarity is usually an important cornerstone for social innovation, although it is no condition for it. Moreover, not all transdisciplinary research automatically contributes to social innovation. Nevertheless, we assume that a higher experience in transdisciplinary research might point to a higher propensity for social innovation.


* A1 strongly correlates with E1 (stakeholder involvement)
* A1 correlates with D1.2 & D1.3 and with D2.3

A1, E1 correlation Matrix:

```{r, echo = FALSE, fig.fullwidth = TRUE}
pairs.panels(a1e1.df, 
             method = "pearson", # correlation method
             hist.col = "#00AFBB",
             density = TRUE,  # show density plots
             ellipses = TRUE, # show correlation ellipses
             stars = TRUE,
             lm = TRUE
             )

```
A1, D1.2, D1.3, D2 correlation Matrix

```{r, echo = FALSE, fig.fullwidth = TRUE}
pairs.panels(a1.df[, setdiff( colnames(a1.df), e1.colnames)], 
             method = "pearson", # correlation method
             hist.col = "#00AFBB",
             density = TRUE,  # show density plots
             ellipses = TRUE, # show correlation ellipses
             stars=TRUE,
             lm = TRUE
             )

# , "e1_diff_res", "civsoc.policy.citiz.welfare", "welfare.nonAcademy"
```

## A1: Factor analysis

There are 2 possible approaches for factor analysis. Either with including all possible variables or analysing each correlation in its own factor analysis but I am including all of those here.

Find the optimal number of factors:

```{r echo=FALSE, fig.fullwidth = TRUE}
# Find the optimal number of factors
a1.ev <- eigen(cor(na.omit(a1.df)))
a1.ns <- nScree(x = a1.ev$values)
plotnScree(a1.ns) # ~4
```


```{r, echo=FALSE}
# Apply factor analysis
a1.fit <- factanal(na.omit(a1.df), 3, rotation = "varimax")
a1.fit


```

## A1: Var. combination

According to the correlation matrix and factor analysis, following in E1 can be combined:

* Representatives of civil soc. orgs
* Policymakers
* Citizens
* Welfare, education workers

```{r}
a1.df$civsoc.policy.citiz.welfare <- (a1.df$groupsInvolved.civsoc. + a1.df$groupsInvolved.policy. + a1.df$groupsInvolved.welfare. + a1.df$groupsInvolved.citiz. )/4 


```

Another approach could be taking the whole variable as stakeholder engagement (other than researchers)

```{r}
a1.df$e1_diff_res <- (a1.df$groupsInvolved.civsoc. + a1.df$groupsInvolved.policy. + a1.df$groupsInvolved.welfare. + a1.df$groupsInvolved.citiz. + a1.df$groupsInvolved.busi. + a1.df$groupsInvolved.media.)/6 

```



Also from the D questions, following variables show strong correlation

* Motivation for welfare
* Non academic benefit pursuit

```{r}
a1.df$welfare.nonAcademy <- (a1.df$groupsInvolved.welfare. + a1.df$benefitForNonAcademy)/2
```

Correlation after combination:

```{r, fig.fullwidth = TRUE}
pairs.panels(a1.df[, c("transdisciplinaryExp.rate.", 
                       "civsoc.policy.citiz.welfare", 
                       "groupsInvolved.busi.",
                       "groupsInvolved.media.",
                       "welfare.nonAcademy",
                       "motivation.prob."
                       )], 
             method = "pearson", # correlation method
             hist.col = "#00AFBB",
             density = TRUE,  # show density plots
             ellipses = TRUE, # show correlation ellipses
             lm = TRUE
             )

```


## A1: Linear Model

Explaining stakeholder involvement with the transdisciplinary experience does not make much sense. Transdisciplinary research should involve stakeholder engagement anyways. We can only compare the effect of the motivation variables with the effect of transdisciplinarity

```{r echo=FALSE, fig.fullwidth=TRUE}
a1.lm <- lm(data = a1.df, civsoc.policy.citiz.welfare ~ motivation.prob. + motivation.welfare. + transdisciplinaryExp.rate. )
tab_model(a1.lm)
```

A linear model with the whole e1 combination:

```{r echo=FALSE}
a1.lm2 <- lm(data = a1.df, e1_diff_res ~ motivation.prob. + motivation.welfare. + transdisciplinaryExp.rate. )
tab_model(a1.lm2)
```

# Example 2: C1 | Problem: Too many independent variables with multicollinearity -> Unstable models
**Hypothesis**:  The self-assessment is an important variable to identify the contribution to social innovation. The higher the self-assessment is the higher is probably the real contribution to social innovation. We assume, however, a trend towards under estimation. Therefore, it is important to confront the self-assessment with other indicators.

* Relation with E1 (stakeholder engagement)
* Relation with D1.2 and D1.3

## Inner corelations in E1
```{r, fig.fullwidth = TRUE}
corr_matrix_plt(e1.df[, -1])
```

* Combine `civsoc` `policy` `citit` `welfare`

```{r}
head(e1.modf_civil)
```

## Inner correlations in D1.2 and D1.3

```{r, fig.fullwidth = TRUE}
corr_matrix_plt(d1.df[, c(2,3)])

```

## Correlation Matrix of C1 with modified E1 and D1.2/3

```{r, fig.fullwidth = TRUE}
corr_matrix_plt(cbind(c3.df, e1.modf_civil, d1.df[, c(2,3)]))

```
## LR Model

#### Alternative 1
```{r echo=FALSE}
c3_lm_df <- as.data.frame(cbind("c3" = c3.df,
                  "bus" = e1.modf_civil$bus,
                  "med" = e1.modf_civil$med,
                  "civ" = e1.modf_civil$civ,
                  "motivation.prob." = d1.df$motivation.prob.,
                  "motivation.welfare." = d1.df$motivation.welfare.)
)


c3_lm <- lm(data=c3_lm_df, c3 ~ bus + med + civ + motivation.prob. + motivation.welfare. + civ:motivation.welfare.)
tab_model(c3_lm, p.style = "numeric_stars")


```

#### Alternative 2
```{r echo=FALSE, fig.fullwidth=TRUE}
c3_lm_alt <- lm(data=c3_lm_df, c3 ~ civ + motivation.prob. + motivation.welfare. + civ:motivation.welfare.)
tab_model(c3_lm_alt, p.style = "numeric_stars")

```
`r margin_note("Mehrere Variablen sind fast unmöglich, Vorschlag?")`

```{r echo=FALSE, fig.fullwidth = TRUE}
library(car)
avPlots(c3_lm_alt)
```


# Example 3: D1 | Problem: What are we modeling &  ?Water is wet?

Hypothesis: The motivation to directly address a natural, technical economic or social problem or even to improve the human condition/welfare can be a strong component for social innovation, although it is not a pre-condition. The motivation to better understand a natural, technical, economic or social phenomenon, however, points to a rather “regular” scientific motivation, without directly aiming to problem solving or improving human/welfare conditions. 

RE-formulation: Motivation for address a natural, technical economic or social problem or even to improve the human condition/welfare are more likely to produce to new or better services, products, processes, or ways of doing things compared to motivation to better understand a natural, technical, economic or social phenomenon.

We have 3 different variables in D1:
```{r echo=FALSE}
d1.colnames

```



How do the independent variable correlate against each other `r margin_note("Should we handle the collinearity between the dependent variables? We want to combine the last 2 but the first 2 correlate better")`

```{r echo=FALSE, fig.fullwidth=TRUE}
# Create d1 df
d1.df <- data[, d1.colnames]

corr_matrix_plt(d1.df)

```

Dependent variable G1: To what degree has your project directly contributed to new or better services, products, processes, or ways of doing things that were targeted towards ...

```{r}
head(g1.df)
```

```{r echo=FALSE,  fig.fullwidth=TRUE}
corr_matrix_plt(g1.df)
```

Combining g1's all sub-variables other than acad. into 1 single variable for **testing purposes**

```{r fig.fullwidth=TRUE}
library(plotly)
barplot(table(g1.modf_civil))
```
Correlation between D1 variables and G1

```{r fig.fullwidth=TRUE}
d1.test.df <- as.data.frame(cbind(d1.df, 
                                  "civ.prod" = g1.modf_civil))

corr_matrix_plt(d1.test.df)
```

LM model 

```{r}
d1.test.lm <- lm(data = d1.test.df, civ.prod ~ motivation.pheno. + motivation.prob. + motivation.welfare. )

tab_model(d1.test.lm)

```

What do we found out: Social motivation produces products for society?

# Example 4: E1 | Relatively straight forward

```{r}
corr_matrix_plt(cbind(data$familiarWithSI.response., e1.df$groupsInvolved.res., e1.df_trans))



```

```{r}
corr_matrix_plt(cbind(e1.df_trans, data$familiarWithSI.response., data$transdisciplinaryExp.rate., d1.df[, 2:3]))
```

```{r}
e1.df_model <- data.frame(cbind(e1.df_trans, data$familiarWithSI.response., data$transdisciplinaryExp.rate., d1.df[, 2:3]))
e1.model <- lm(data=e1.df_model, e1.df_trans ~ data$familiarWithSI.response. + data$transdisciplinaryExp.rate. + d1.df[, 2] + d1.df[, 3])
```

```{r}
summary(e1.model)
```
