---
title: "SIVOCS Interview Candidates | Batch 2"
runningheader: "Selection Criteria" # only for pdf output
subtitle: "" # only for html output
author: ""
date: "`r Sys.Date()`"
output:
  tufte::tufte_book:
    citation_package: natbib
    latex_engine: xelatex
    keep_tex: true
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
  tufte::tufte_html: default
bibliography: skeleton.bib
link-citations: yes
---

```{r setup, include=FALSE}
library(tufte)
library(ggplot2)
library(tidyr)
library(scales)
library(ggthemes)
library(ggthemr)
library(gridExtra)
library(stringr)
# invalidate cache when the tufte version changes
knitr::opts_chunk$set(cache.extra = packageVersion('tufte'))
options(htmltools.dir.version = FALSE)
# why do I even have to do this
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())

g_tick_size_main <- 9 
g_tick_size_side <- 7 
```


```{r include=FALSE}
df_ult <- readRDS("./batch2.1.RDS")
source("./02_analysis/02_static_responses.R")

```


# Selection

The second batch of interview candidates focuses on unusual or unexpected cases along with the projects that scored high in one or multiple SI-related variables. There are 2 main clusters that encapsulate the selection process; Cluster 1 is generally concerned with the projects that have been relatively high rated regarding multiple outcome variables despite having low ratings in other key SI variables or vice versa and Cluster 3 includes the projects that have overall high rating in key SI variables. 

The criteria used for each cluster is as follows.

## Cluster 1 (19 projects): 

* Low motivation to benefit society - High SI contribution (self-assessment)
* Low transdisciplinary involvement - High public outcome
* Low motivation to improve human condition - high impact statement on emancipation/ capability/ understanding


## Cluster 3 (12 projects):

* High motivation to imp. human condition + changed behaviour (public, policy, civil society orgs)
* High SI familiarity (and/or high overall SI stats)

## Final

After a manual elimination, from the ~80 selected projects, approximately 38 relatively less related projects are eliminated, **leaving 42 respondents in total** (12f | 29 ~ 30%).


```{r gender, echo=FALSE, message=FALSE, warning=FALSE}
gen <- as.data.frame(table(df_ult$gender))
g <- ggplot(gen, aes(x=Var1, y=Freq))+
  #theme_fivethirtyeight()+
  #theme_calc()+
  scale_x_discrete(breaks= pretty_breaks())



# Number of cars in each class:

g + 
  geom_col(fill="#D32F49") + 
  theme_light() +
   theme( axis.text.y = element_text( 
                         size=g_tick_size_side), axis.text.x = element_text(
                         size=g_tick_size_side), axis.title=element_text(size=g_tick_size_side), legend.text=element_text(size=g_tick_size_side)) + geom_text(aes(label=Freq), vjust=1.6, color="white", size=5) +
scale_x_discrete("") + 
  scale_y_continuous("count") 
 
```

Also, the distribution of the sci. domains in the final sample is as follows:



```{r echo=FALSE, fig.fullwidth = TRUE}
gen <- as.data.frame(table(df_ult$domain))
gen$Var1 <- as.vector(gen$Var1)
gen$Var1[3] <- "Math., Natural- and Eng. Sci."
gen$Var1[2] <- "HSS"
g <- ggplot(gen, aes(x=Var1, y=Freq))



# Number of cars in each class:

g + 
  geom_col(fill="#338BBE") + 
  theme_light() +
  theme( axis.text.y = element_text( 
                         size=g_tick_size_side), axis.text.x = element_text(
                         size=g_tick_size_side), axis.title=element_text(size=g_tick_size_side), legend.text=element_text(size=g_tick_size_side)) + geom_text(aes(label=Freq), hjust=1.6, color="white", size=5) +
scale_x_discrete("") + 
  scale_y_continuous("count") +
  coord_flip() 

```

