---
title: "SIVOCS | Model building"
output:
  html: default
  github_document: default
---

```{r setup, include=FALSE}
source("./02_analysis/02_static_responses.R")
# Load the feature importances from python script
feature_list <- read.csv("./02_analysis/PFA_feature_importance.csv")

```

```{r include = FALSE}
library(psych)
library(plotly)
```


## Principal Feature Analysis

> In some applications it might be desired to pick a subset of the original features rather then find a mapping that uses all of the original features. The benefits of finding this subset of features could be in saving cost of computing unnecessary features, saving cost of sensors (in physical measurement systems), and in excluding noisy features while keeping their information using “clean” features (for example tracking points on a face using easy to track points- and inferring the other points based on those few measurements).


How does the algorithm look like:

```python:

class PFA(object):
    def __init__(self, n_features, q=None):
        self.q = q
        self.n_features = n_features

    def fit(self, X):
        if not self.q:
            self.q = X.shape[1]

        sc = StandardScaler()
        X = sc.fit_transform(X)

        pca = PCA(n_components=self.q).fit(X)
        A_q = pca.components_.T

        kmeans = KMeans(n_clusters=self.n_features).fit(A_q)
        clusters = kmeans.predict(A_q)
        cluster_centers = kmeans.cluster_centers_

        dists = defaultdict(list)
        for i, c in enumerate(clusters):
            dist = euclidean_distances([A_q[i, :]], [cluster_centers[c, :]])[0][0]
            dists[c].append((i, dist))

        self.indices_ = [sorted(f, key=lambda x: x[1])[0][0] for f in dists.values()]
        self.features_ = X[:, self.indices_]
```

##  Results of PFA

* PFA has been looped **1000** times, feature frequencies are as follows


```{r}

fig <- plot_ly(x = feature_list$X1, y = feature_list$X0, type = 'bar', orientation = 'h')

fig
```





```{r pressure, echo=FALSE}
features_to_rm <- tail(feature_list$X0, 40)
features_to_rm
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
