---
title: "SIVOCS"

subtitle: ""

date: ""
 
institute: ""

output:
  xaringan::moon_reader:
    self_contained: TRUE
    css: [default, metropolis, metropolis, metropolis-fonts]
    #css: [robot, robot, robot-fonts]
    #css: [default, metropolis, default-fonts, "mtheme.css", "fonts_mtheme.css"]
    #css: [default, metropolis, default-fonts]
    #css: xaringan-themer.css
    
    lib_dir: libs
    nature:
      nature:
      highlightStyle: github
      highlightLines: true
      highlightSpans: true
      countIncrementalSlides: false
      ratio: "16:9"
    background-image: url(../../doc/zsi_logo.svg)
    background-position: 0% 100%
    background-size: 30%

---

<style>

.center2 {
  margin: 0;
  position: absolute;
  top: 50%;
  left: 50%;
  -ms-transform: translate(-50%, -50%);
  transform: translate(-50%, -50%);
}

.large { font-size: 130% }
.small { font-size: 70% }

.remark-slide-content.hljs-default {
  border-top: 60px solid #23373B;
}

.remark-slide-content > h1 {
  font-size: 30px;
  margin-top: -75px;
}

</style>


```{r setup, include = FALSE}
library(tufte)
# invalidate cache when the tufte version changes
knitr::opts_chunk$set(
	message = FALSE,
	warning = FALSE,
	cache.extra = packageVersion("tufte")
)
options(htmltools.dir.version = FALSE)
library(dplyr)
library(plyr)
library(ggplot2)
library(ggbeeswarm)
library(plotly)
library(magrittr)
library(ggplot2)
library(PerformanceAnalytics)
library(psych)
library(corrplot)
library(nFactors)
library(kableExtra)
require(ggiraph)
require(ggiraphExtra)
require(plyr)
library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(tidyverse)
library(gt)
library(grid)
library(ggpubr)
library(psych)
library(GPArotation)
library(car)
library(candisc)
library(jtools)
library(formattable)
# Activate likert and plyr
library(likert)
library(plyr)
library(ggcorrplot)
library(waffle)
library(hrbrthemes)
library(tidyverse)
library(scales)
library(sjPlot)
library(sjmisc)
library(sjlabelled)

setwd("/home/ubd/Nextcloud/utku_SIVOCS")
# Data Frame
source("./02_analysis/02_static_responses.R")
# colnames of the specific question groups
source("./02_analysis/99_question_groups.R")
# A good table to display factor analysis
source("https://raw.githubusercontent.com/franciscowilhelm/r-collection/master/fa_table.R")

den <- read.csv("./01_data/sample_meta.csv")

domain_colors <- c("#FC4E07", "#E7B800", "#00AFBB")
knitr::opts_chunk$set(fig.retina=2, echo=FALSE, dev='svg')

data$domain[data$domain == unique(data$domain)[1]] <- "Math., Natur. and Eng. Sci."

g_tick_size_main <- 14
g_tick_size_side <- 12

```

# B1 (NEW): Kruskal-Wallis test: SI familiarity depends on sci. domains?



```{r echo=FALSE}
bartlett.test(data=data, familiarWithSI.response. ~ domain)



```


```{r}
kwtest <- kruskal.test(data=data, familiarWithSI.response. ~ domain)
kwtest

```

* Mean ranks of the groups are not the same, SI fam. depends on domain

---

## 
##     Bartlett test of homogeneity of variances
## 
## data:  familiarWithSI.response. by domain
## Bartlett's K-squared = 12.931, df = 2, p-value = 0.001556

---

# B1: Wilcox test: SI familiarity depends on sci. domains?

.pull-left[
* SSH vs other

```{r echo=FALSE}
b1domain.df <-data.frame(familiarWithSI = data$familiarWithSI.response.,
                         domain =  data$domain)


b1.wilcox <- wilcox.test(data=data, familiarWithSI.response. ~ SSH, mu = 0, alt = "two.sided", conf.int = T, conf.level = 0.95, paired = F, exact =  T, correct = T )
b1.wilcox

```

]

.pull-right[
* NS vs other


```{r echo=FALSE}
b1domain.df <-data.frame(familiarWithSI = data$familiarWithSI.response.,
                         domain =  data$domain)


b1.wilcox <- wilcox.test(data=data, familiarWithSI.response. ~ Math._Natur._and_Eng., mu = 0, alt = "two.sided", conf.int = T, conf.level = 0.95, paired = F, correct = T )
b1.wilcox

```
]

---
# Pairwise Wilcox

```{r}
b1.wilcox <- pairwise.wilcox.test(data=data, familiarWithSI.response. ~ Math._Natur._and_Eng., mu = 0, alt = "two.sided", conf.int = T, conf.level = 0.95, paired = F, correct = T, p.adjust="bonferroni" )
b1.wilcox

```


---

# B1: *Familiarity with SI* across scientific domains

<br>

```{r echo=FALSE, fig.width=12, fig.height=4, dev='svg', fig.retina=2, fig.align='center'}
b1domain.df <-data.frame(familiarWithSI = data$familiarWithSI.response.,
                         domain =  data$domain)

b1domain.df$familiarWithSI <- as.numeric(b1domain.df$familiarWithSI)
b1domain.df %>% 
  gather(key="domain", value="familiarWithSI") %>%
  ggplot( aes(x=familiarWithSI, y=domain, fill=domain),  show.legend = FALSE) +
    geom_boxplot() +
  ylab(" ")+
  theme_light() + 
  theme(axis.text.y=element_blank())+ scale_fill_discrete(name = "Domain") + xlab("Familiarity with SI") + scale_fill_manual(values=c("#FC4E07", "#E7B800", "#00AFBB"), name="Domain") +
  scale_x_continuous(breaks = seq(0,10,2))  

```
<br>
<br>

* *Familiarity with SI* differs across scientific domains (ANOVA test: p &lt; 0.05)
* *Biology and Medicine* and *Math., Natur, and Eng. Sci.* are similar (pairwise t-test: p &gt; 0.05)
* *Humanities and Social Sciences* are significantly different than the others (pairwise t-test with each: p &lt; 0.05)

